
1/Merge the training and the test sets to create one data set


a)Load all data into R

```{r}
library(readr)
library(dplyr)

train <- read_table("./UCI HAR Dataset/train/X_train.txt",col_names = FALSE)
train_subject <- read_table("./UCI HAR Dataset/train/subject_train.txt",col_names = FALSE)
features <- read_table("./UCI HAR Dataset/features.txt",col_names = FALSE)
train_activities <- read_table("./UCI HAR Dataset/train/y_train.txt",col_names = FALSE)
test <- read_table("./UCI HAR Dataset/test/X_test.txt",col_names = FALSE)
subject_test <- read_table("./UCI HAR Dataset/test/subject_test.txt",col_names = FALSE)
activity_test <- read_table("./UCI HAR Dataset/test/y_test.txt",col_names = FALSE)
activity_labels <- read_table("./UCI HAR Dataset/activity_labels.txt",col_names = FALSE)
```

b) recompose the total train dataset with subject and activity number

```{r}
train_total <- cbind(train_subject,train_activities,train)
```


c)recompose the total test dataset with subject and activity number

```{r}
test_total <- cbind(subject_test,activity_test,test)
```

d) label columns

  i) modify format features data by removing the number at the beginning of each row

```{r}
featuress <- gsub("^[0-9][0-9]?[0-9]? ","",features[[1]]) #gsub replace the numbers by nothing.
head(featuress) #gsub returns a list
```

```{r}
tfeatures <- t(featuress) #transpose featuress into a matrix with one line
```

  ii)labl columns of train_total and test_total datasets
  
```{r}
colnames(train_total,do.NULL=TRUE)
colnames(train_total) <- c("subject","activity",tfeatures)
colnames(test_total,do.NULL=TRUE)
colnames(test_total) <- c("subject","activity",tfeatures)
head(train_total)
```

e) merge train_total and test_total datasets

```{r}
train_test <- rbind(train_total,test_total)
```


2) Extract only the measurements on the mean and standard deviation for each measurement. 

a) remove special characters ("-") in column names

```{r}
valid_column_names <- make.names(names=names(train_test), unique=TRUE, allow_ = TRUE)
names(train_test) <- valid_column_names
```

b) select columns with the name containing the words "mean" or "sd"
```{r}
train_test_sub <- select(train_test,subject, activity,contains("mean"),contains("std")) 
head(train_test_sub)
```


3) Uses descriptive activity names to name the activities in the data set

a) lower capitals and remove "_" in activity names 

```{r}
activity_labels <- lapply(activity_labels, function(x) tolower(x))
activity_labels <- lapply(activity_labels,function(x) gsub("_"," ",x))
activity_labels #lapply returns a list
```

b) transform list back to data frame

```{r}
activity_labels <- data.frame(activityNr=activity_labels$X1,activity=activity_labels$X2)
activity_labels
```

c) merge activity data frame with the test_total data frame

```{r}
test_train_label <- merge(activity_labels,train_test_sub,by.x="activityNr",by.y="activity",all=TRUE)
head(test_train_label)
```

d) drop the "activityNr" column

```{r}
drop <- "activityNr"
test_train_label <- test_train_label[ , !(names(test_train_label) %in% drop)]
head(test_train_label)
```


5) From the data set in step 4, creates a second, independent tidy data set with the average of each variable for each activity and each subject.


```{r}
test_train_label_2 <- summarize_all(group_by(test_train_label,activity,subject),funs(mean))
head(test_train_label_2)
```

```{r}
write.table(test_train_label_2,file="./TidyDataset.txt",row.name=FALSE)
```
